Lattice studies of strongly coupled gauge theories started with the pioneering work of 
Wilson. The success of lattice QCD since then has improved our understanding of the strong dynamics, 
crucial for a proper understanding of many interesting phenomena in Physics. However, it is now known that the 
Standard model is only an approximation to some richer underlying theory. It is
believed that supersymmetry has a special role to play in the framework of that theory. 
Even if nature is non-supersymmetric at all energy scales and we see no experimental evidence 
in the coming decades, the beautiful structure of these theories
and the great failure could still be very important lessons in our quest to understand the universe. 
In four dimensions, one particular supersymmetric theory has drastically altered our understanding 
of the holographic principle. In view of these observations, the study of supersymmetric
theories on lattice at strong couplings is crucial. Even though lattice supersymmetry has a long history 
going back four decades, it has been very difficult to simulate four-dimensional theory at strong
couplings till date. This is because supersymmetry on the lattice is far from being trivial and is broken 
even at the classical level because of the supersymmetric algebra.
However, substantial progress has been made in studying these theories on the lattice over the
past decade. Several wonderful ideas like topological twisting, differential forms, point group 
symmetries of the lattice and integer form fermions all come together and has enabled us to study
 these supersymmetric theories by preserving a subset of supersymmetries exactly on the lattice. 
This thesis deals with the numerical studies of super Yang-Mills (SYM) theories in various dimensions, 
their large $N$ limit, and the relation to gauge/gravity dualities. 