\vspace*{2em}
I am thankful to my advisor Simon Catterall for his support, encouragement, and 
numerous conversations during which I learned how to 
think about a problem in Physics. He has also instilled in me, a taste for 
intuition and simplicity, and to see the Physics rather than getting fazed by 
unimportant details. He gave me two of his invited talks at YITP Kyoto 
(probably the best time of the year during sakura!) and ICTS Bangalore. He has been 
very patient with me and let me work mostly on my own in the last few years. 
I have benefited from my interactions with Toby Wiseman, who explained to me various things
over our numerous Skype calls and in person at Kyoto. His approach towards solving a problem and finding 
opportunities in despair have taught me a lot. I am thankful to Joel Giedt for multiple interactions 
and wonderful suggestions which has immensely contributed to my understanding.  
I have also spent time working with Jack Laiho on Euclidean dynamical triangulations and would like to thank
him. When I started working on lattice supersymmetric theories, 
I was fortunate to have David Schaich (359 PB) in the office next to me and I 
have learned a lot from him and would like to thank him. In the last two years, 
I have enjoyed multiple discussions on tensor networks and table-tennis games 
with Judah F. Unmuth-Yockey and would like him to thank him. I would like to thank 
Jay Hubisz, Cristian Armendariz-Picon, and Scott Watson 
for the wonderful courses they taught in graduate school. I am also thankful to 
Carl Rosenzweig who was the instructor for my first TA class (PHY 101 labs!) in the Fall 
of 2013 and for his reminiscences about QCD from the 1970s during our weekly group meetings.
I am grateful to A.P. Balachandran for his useful remarks and comments during my presentations 
and talks. I am thankful to Anosh Joseph, Masanori Hanada, Ethan Neil for
making arrangements for my talks at ICTS Bangalore, YITP Kyoto, and UC Boulder in 
the past two years.  
I would like to thank Abhinav Gupta, Bikram Phookun, and Vikram Vyas for undergraduate classes at  
St. Stephen's College, Delhi (2007-2010). I am grateful to Shobhana Narasimhan for support during my time
in Bangalore (2009-2010). During 2010-2011, I worked on nano-materials and related topics at UPMC, 
Paris. I interacted with M. Marangolo, N. Witkowski, F. Mauri, and M. Calandra during that year and would like
to thank them for their help. For my time in Calcutta (2011-2013), 
I am thankful to Shibaji Banerjee, Sarbari Guha, and Suparna Roychowdhury and my friends during that time - 
Ripon, Soumen, Arghajit, Dibyajyoti, Sangita, Yeasin, Soumyadeep. 
I would like to thank my undergraduate friends (in random order) who have now been friends for 
more than ten years: Bahul, Uddipta, Anjishnu, Soumyodipto, Rajarshi, Rahul, Parul, Varun, 
Ravi Kunjwal, Debayan, Arijit, and Chitraleema. Though I met all of them for the first time in Delhi, the 
last time I met them was either in 
New York, Paris, Athens, Berlin, Austin, Toronto, or London. I would like to thank friends after 
August 2013 (in random order): Prashant, Nouman, Sudipta, Prabesh, Francesco, Suraj Shankar, Swetha, 
Aarti, Bithika, Jayanth, Gizem, Cem, Scott, Mahesh, Asad, and Sourav. 
A friend in Syracuse with whom I have spent hours working in offices next to each 
other (361 \& 363 PB)\footnote{For the curious reader: The room numbers $n$ on 3rd floor facing the 
Archbold Gymnasium are $\textit{n}$ mod 2 = 1} in 
the department is Ogan \"{O}zsoy. I enjoyed our discussions and would like to thank him. I would 
also like to thank A.R.Rahman for his compositions which have comforted me through the tough times. 
I wish him `Bharat Ratna' in the future. I would like to thank my wife, Kriti, for her support and 
apologize for the times when I was completely immersed in the work at odd 
hours of the day. At last, I would like to thank my parents and family for believing in me and encouraging me 
at every step in my life and teaching me the value of education and allowing me to pursue basic sciences 
instead of more lucrative professional careers also available to me in 2007. This thesis won't have been possible 
without their unending love and warmth. I am sorry to other wonderful people whom I might have missed to 
mention here, for they will know that my affection and gratitude is not just restricted to this space and time 
of my life.
